---
title: "01-language-basics"
output: html_notebook
---

## Markdown Basics

Try executing a code chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file

## Language Basics

### Assignment operators

R have 3 different assignment operators. I have seen using `<-` operator the most on internet but my personal preference is to use `=` operator. The last operator is rarely used.

```{r}
x <- 10
x = 10
10 -> x
```

### Print

You can use the `print` function to print a value explicitly otherwise calling the variable also prints its value implicitly.

```{r}
print(x)
x
```

### Variables

There are several veriable types in R

```{r}
b = TRUE
i = 123L
n = 12.34
s = "Imran Pollob"
b
i
n
s
```


### Function

```{r}
foo = function(x) {
  x + 1
}

foo(2)
```

### Vector

```{r}
v = c(1, 2, 3)
v
```

### Sequence

```{r}
sequence = 1:10
sequence
```

### Matrix

```{r}
m = matrix(data=1:6, nrow=2, ncol=3)
m
```

### Array

```{r}
a = array(data=1:8, dim=c(2, 2, 2))
a
```

### List

```{r}
l = list(TRUE, 1, 12.34, "ABc")
l
```

### Factor

```{r}
f = factor(c('boy', 'girl', 'boy', 'boy', 'girl'))
f
levels(f)
unclass(f)
```

### Data Frame

```{r}
df = data.frame(
  name = c('Boy', 'Girl', 'Young'),
  age= c(5, 12, 19),
  isAdult = c(FALSE, FALSE, TRUE)
)

df
```

```{r}
df[1, 2]
```

```{r}
df[1, ]
```

```{r}
df[ , 2]
```

```{r}
df[["age"]]
```

```{r}
df$age
```

```{r}
df[c(1, 2), ]
```

```{r}
df[1:2, ]
```

```{r}
df[c(TRUE, TRUE, FALSE), ]
```
```{r}
df[df$isAdult == TRUE, ]
```

```{r}
df[df$age < 18, ]
```

```{r}
df[df$name %in% 'Boy', ]
```

```{r}
df[df$name %in% c('Boy', 'Girl'), ]
```

### Vector Operation

```{r}
c(1, 2, 3) + c(1, 1, 1)
```

### Named vs Ordered Arguments

```{r}
m <- matrix(data = 1:6, nrow = 2, ncol = 3)
n <- matrix(1:6, 2, 3) 
m == n
identical(m, n)
```

### Installing Packages

```{r}
install.packages('rmsfact')
```

### Importing package

```{r}
library(rmsfact)
```



### Remove package

```{r}
remove.packages('rmsfact')
```










